Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes

### 2019-01-24 Paper/AgreementAttraction.Rmd
paperwriting

```{r outline, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Introduction
Recap on what Lago did
My experiment
  Reasoning
  Experiment Details
    Environments
    Items
    Fillers
    Participants
    Exclusions
    Results and Discussions
  ...

@@

\ex \underline{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.

@@

They have found a significant effect of number attraction in Turkish ranging between 11%--15% across monolinguals. As seen from the results of statistical analysis in Table (\ref{lagomodel}), acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number which indicates an number attraction effect.

\begin{table}[]
\centering
\begin{tabular}{llcccc}
\hline
    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
\end{tabular}
\caption{Model results for the judgments of monolingual cited from @Lago.}
\label{lagomodel}
\end{table}

@@

However, we argue that not only genitive case but also possessive case plays a significant role in delivering the case information. None of the experimental items in @Lago has a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive.

## Modifications
## Participants
## Filler Items
## Results and Discussion

>>>>

```{r init, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(languageR)
library(tidyverse)
library(gdata)
library(MASS)
library(magrittr)
library(ggplot2)

data <- read.csv('results', 
                 header = F, 
                 comment.char = "#", 
                 encoding = "UTF-8" , 
                 col.names = paste0("V",seq_len(11)), 
                 fill = TRUE)

colnames(data) = c("Time", "MD5", "ControllerType", "SentenceNoInStimFile", "Element", "Type", "Item", "Sentence", "Question","Answer", "RT")

FormEntries <- subset(data, ControllerType != "DashedAcceptabilityJudgment" ) %>% drop.levels(); nrow(data)
data %<>% subset(ControllerType == "DashedAcceptabilityJudgment")
age <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
  dplyr::filter(Sentence == "age") %>%
  dplyr::select(MD5, Age = Question)
natturk <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
  dplyr::filter(Sentence == "natturk") %>%
  dplyr::select(MD5, Natturk = Question) %>%
  mutate(Natturk = Natturk == "male")
dex <- dplyr::select(FormEntries, MD5,Sentence,Question) %>% 
  dplyr::filter(Sentence == "dex") %>%
  dplyr::select(MD5, Dex = Question) %>%
  mutate(Dex = ifelse(Dex == "male", "right-handed", "left-handed"))
FormPart <- dplyr::left_join(age, natturk, by = "MD5") %>% 
  dplyr::left_join(., dex , by = "MD5" ) %>% 
  unique()
lenForm <- length(levels(factor(FormPart$MD5))); lenForm
md5form <- levels(factor(FormPart$MD5))
md5form_subject <- data.frame("MD5" = md5form, "Subject" = sprintf("S[%s]",seq((lenForm))))
FormPart <- merge(FormPart,md5form_subject, all = T)

stopifnot( nrow(data) %% 2 == 0 )
rows_stim <- data[c(T,F),]
rows_resp <- data[c(F,T),]

data <- rows_resp %>% left_join(md5form_subject) %>% dplyr::select(-MD5, -Time, -ControllerType, -Sentence, -Element) %>%
  dplyr::rename(ResponseCorrect=Answer, Response=Question)
data %<>% group_by(Subject) %>% mutate(trial_no = seq(Subject))
data %<>% within({ late_response = (Response == "NULL")
Response[late_response] = NA
ResponseCorrect[late_response] = NA
})

responses <- c(yes="İYİ (P'ye basınız)", no="KÖTÜ (Q'ya basınız)")
stopifnot( all(data$Response %in% responses | is.na(data$Response) ) )

data$ResponseYes <- ifelse(grepl("P",data$Response) , T, 
                           ifelse(grepl("Q",data$Response) , F, NA))

data$condition <- 
  with(data, case_when(Type == "filler" & SentenceNoInStimFile >= 200 ~ "a",
                       Type == "filler" & SentenceNoInStimFile < 200 ~ "b",
                       Type == "condition_a" ~ "a",
                       Type == "condition_b" ~ "b",
                       Type == "condition_c" ~ "c",
                       Type == "condition_d" ~ "d",
                       TRUE ~ as.character(NA)))
data$experiment <- ifelse(data$Type %in% c("condition_a", "condition_b", "condition_c", "condition_d"), "AgrAttr", as.character(data$Type))

data %>% group_by(experiment, condition) %>% 
  summarise(perc_yes = mean(ResponseYes, na.rm = T),
            perc_na = mean(is.na(ResponseYes)))

conditions_info <- data.frame(experiment = c("AgrAttr", "AgrAttr", "AgrAttr", "AgrAttr", "filler", "filler"),
                              condition = c("a","b","c","d", "a","b"),
                              grammatical = c("ungram", "gram", "ungram", "gram", "ungram", "gram"),
                              verb_num = c("sg","pl","sg","pl", "sg","pl"),
                              attracted = c(T,T,F,F,F,F),
                              stringsAsFactors = FALSE) 
data %<>% left_join(conditions_info)
data %<>% subset(Type != "practice") %>% drop.levels()

dataAv <- data %>% 
  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
  as.data.frame()

dataAv %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted))

data$trial_group <- Hmisc::cut2(data$trial_no, g=5)

dataAvSplit <- data %>% 
  group_by(experiment, condition, grammatical, verb_num, attracted, trial_group) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
  as.data.frame()

plot_split <- dataAvSplit %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~trial_group)

dataAvBySubj <- data %>% 
  group_by(Subject, experiment, condition, grammatical, verb_num, attracted) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T), N = sum(!is.na(ResponseYes))  )  %>% 
  as.data.frame()
head(dataAvBySubj,10)

dataAvBySubjWide = dataAvBySubj %>% mutate(expcond = paste(experiment,condition, sep="_")) %>% dplyr::select(-experiment, -condition, -avRT, -N, -grammatical, -verb_num, -attracted) %>% tidyr::spread(expcond, p_yes)
dataAvBySubjWide %<>% mutate(delta_dc = AgrAttr_d - AgrAttr_c)
bad_subjects = subset(dataAvBySubjWide, delta_dc <= 0.25 ) %>% .$Subject

dataAvBySubj %>% subset(Subject %in% bad_subjects) %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) + facet_wrap(~Subject)

dataAvClean <- data %>% subset(!Subject %in% bad_subjects)%>% 
  group_by(experiment, condition, grammatical, verb_num, attracted) %>%
  summarize(avRT = mean(RT), p_yes = mean(ResponseYes, na.rm = T)) %>% 
  as.data.frame()

dataAvClean <- slice(dataAvClean, 1:4)

plot_average <- dataAvClean %>% ggplot(aes(grammatical, p_yes, group = paste(experiment,attracted), color = experiment )) + geom_point() + geom_line(aes(linetype =attracted)) #+ facet_wrap(~experiment, scales = "free_y")

@@

\ex \underline{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singers' backup vocalist jumped on the stage non-stop.

@@

They have found a significant effect of number attraction in Turkish ranging between 11%--15% across monolinguals. As seen from the results of statistical analysis in \textsc{Table} (\ref{lagomodel}), acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number which indicates an number attraction effect.

\begin{table}[!hbt]
\centering
\begin{tabular}{llcccc}
\hline
    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
\end{tabular}
\caption{Model results for the judgments of monolingual cited from @Lago.}
\label{lagomodel}
\end{table}

@@

However, our first hypothesis was the possibility of participants engaging in a shallow processing, which ends up in a situation where not only genitive case but also possessive case plays a significant role in delivering the case information. None of the experimental items in @Lago has a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive. Unlike genitive case, the accusative case in Turkish is extremely rare to see on the head noun of the subject, which only occurs in the raising predicates as in example (\ref{dsm}).

\begin{exe}
\ex \label{dsm}
\gll Ben sen-i git-ti-n san-d{\i}-m\\
I you-\textsc{acc} go-\textsc{pst}-\textsc{2Sg} suppose-\textsc{pst}-\textsc{1Sg}\\
\glt I thought you were gone.
\end{exe}

In order to test this hypothesis, we have replicated the @Lago study with modified items, where the possessive is not ambiguous with the accusative case. We have tried to be as faithful as possible to the original sentences while trying to make sentences as plauisable as possible at the same time. We keep the semantic relation between the head nound and the controller the same with   A set of sentences are exemplified below.

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{exp1}
\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
\glt Because of the northeaster, comedian's assistant felt chilly.

\ex \underline{Grammatical, PL attractor} \label{exp2}
\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
\glt Because of the northeaster, comedians' assistant felt chilly.

\ex \underline{Ungrammatical, PL attractor} \label{exp3}
\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
\glt Because of the northeaster, comedians' assistant felt chilly.

\ex \underline{Ungrammatical, SG attractor} \label{exp4}
\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
\glt Because of the northeaster, comedian's assistant felt chilly.

\end{xlist}
\end{exe}

As seen in the examples unlike @Lago's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* one. As for the filler items, we could not used or adapt from the original experimentsince the fillers of the original study were not online. We have used two types filler sentences: a grammatical ones where the verb bears plural agreement (\ref{fillera}), and an ungrammatical one where verb does not bear plural agreement (\ref{fillerb}). We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability, and disregard other elements in the sentences when answering questions.

\begin{exe}
\ex
\begin{xlist}
\ex \label{fillera}
\gll Adam-{\i}n anne-si fena-la\c{s}-{\i}nca inek kurban et-ti-ler.\\
man-\textsc{gen} mother-\textsc{poss} bad-\textsc{vrb}-\textsc{cvb} cow sacrifice do-\textsc{pst}-\textsc{pl}\\
\glt When his mother got ill, (they) sacrificed a cow.
\ex \label{fillerb}
\gll *Pizzac{\i}-n{\i}n kurye-si t\"{o}kezle-yince sos-lar yer-e sa\c{c}-t{\i}.\\
pizzaria-\textsc{gen} courier-\textsc{poss} trip-\textsc{cvb} sauce-\textsc{pl} floor-\textsc{dat} scatter-\textsc{pst}\\
\glt Intended: When the pizza boy tripped, sauces scattered around. 
\end{xlist}
\end{exe}

All of our data, experimental materials, our experiment design, and as well as our fillers can be found at the Center for Open Science Framework website (https://osf.io/).

## Participants and Procedure

One hundred seven Turkish speakers with mean age of X were recruited from the Bogazici University in {\.I}stanbul. We did not collect participants' knowledge of other languages; however, we ensured that Turkish is their native language and they predominantly used in their daily lives. In the experiments, participants are asked to judge the experimental and filler sentences whether or not they sound acceptable in Turkish. All of the sentences were presented one word at a time in the center area of the screen for 500 ms per word unlike @Lago and @Wagers2009, in which researches used 300 ms visual presentation per word. Experiment was run on a web-based platform Ibex Farm, and all of the documentation can be found in our osf and github page.

Before the experiment, they have been instructed to give accurate and quick answers with their own intuition, and they were also notified about the time limit for answering. At the start of the experiment they were given 4 practice items with feedbacks.

What to write about analyze?

## Results and Discussion

In \textsc{Figure} (\ref{fig:replication}), y-axis shows proportion of "acceptable" answers, and x-axis indicates whether or not the sentences in that group is grammatical. Moreover, linetypes indicates an attractor noun with overt plural morphology. As seen from the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and singular verb were accepted by the participants following the findings of @Lago. We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was already shown in @Lago with close results.

In \textsc{Table} (\ref{tab:replication}), ............

\begin{figure}[H]
  \begin{floatrow}
    \ffigbox{%
```{r, fig.align = "right", echo = F}
print{}
```
    }{\caption{A figure}}

    \btabbox{%
```{r, fig.align = "right", echo = F}
knitr::kable(head(mtcars[,1:3]), format = "latex")
```
    }{\caption{A table}}
  \end{floatrow}
\end{figure}

### 2019-01-24 Paper/AgreementAttraction.tex
paperwriting

@@

They have found a significant effect of number attraction in Turkish
ranging between 11\%--15\% across monolinguals. As seen from the results
of statistical analysis in Table (\ref{lagomodel}), acceptability
judgments showed an immense effect of grammaticality, and there is also
interaction between grammaticality and attractor number which indicates
an number attraction effect.

\begin{table}[]
\centering
\begin{tabular}{llcccc}
\hline
    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
\end{tabular}
\caption{Model results for the judgments of monolingual cited from @Lago.}
\label{lagomodel}
\end{table}

According to Lago (2018)'s stipulation, Turkish genitive case does not
provide a strong cue against subjecthood since it is extremely common to
see genitive marked subjects in Turkish embedded clauses, as in example
(\ref{gensubj}).

@@

@@

\hypertarget{modifications}{%
\subsection{Modifications}\label{modifications}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{filler-items}{%
\subsection{Filler Items}\label{filler-items}}

\hypertarget{motivation-1}{%
\subsection{Motivation}\label{motivation-1}}

@@

>>>>

% for figure and table side by side
\usepackage{floatrow}
\newfloatcommand{btabbox}{table}

@@

They have found a significant effect of number attraction in Turkish
ranging between 11\%--15\% across monolinguals. As seen from the results
of statistical analysis in \textsc{Table} (\ref{lagomodel}),
acceptability judgments showed an immense effect of grammaticality, and
there is also interaction between grammaticality and attractor number
which indicates an number attraction effect.

\begin{table}[!hbt]
\centering
\begin{tabular}{llcccc}
\hline
    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
\end{tabular}
\caption{Model results for the judgments of monolingual cited from @Lago.}
\label{lagomodel}
\end{table}

According to Lago (2018)'s stipulation, Turkish genitive case does not
provide a strong cue against subjecthood since it is extremely common to
see genitive marked subjects in Turkish embedded clauses, as in example
(\ref{gensubj}). Unlike English, genitive case is compatible with the
subjecthood in English. Thus, Lago (2018) attributes the robust
agreement attraction effects to the case information.

@@

However, our first hypothesis was the possibility of participants
engaging in a shallow processing, which ends up in a situation where not
only genitive case but also possessive case plays a significant role in
delivering the case information. None of the experimental items in Lago
(2018) has a head noun which ends with a vowel; thus, all of the
possessive markers are morphologically and phonologically ambiguous
between the accusative case and the possessive. Unlike genitive case,
the accusative case in Turkish is extremely rare to see on the head noun
of the subject, which only occurs in the raising predicates as in
example (\ref{dsm}).

\begin{exe}
\ex \label{dsm}
\gll Ben sen-i git-ti-n san-d{\i}-m\\
I you-\textsc{acc} go-\textsc{pst}-\textsc{2Sg} suppose-\textsc{pst}-\textsc{1Sg}\\
\glt I thought you were gone.
\end{exe}

In order to test this hypothesis, we have replicated the Lago (2018)
study with modified items, where the possessive is not ambiguous with
the accusative case. We have tried to be as faithful as possible to the
original sentences while trying to make sentences as plauisable as
possible at the same time. We keep the semantic relation between the
head nound and the controller the same with A set of sentences are
exemplified below.

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{exp1}
\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
\glt Because of the northeaster, comedian's assistant felt chilly.

\ex \underline{Grammatical, PL attractor} \label{exp2}
\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}.\\
comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-$\varnothing$\\
\glt Because of the northeaster, comedians' assistant felt chilly.

\ex \underline{Ungrammatical, PL attractor} \label{exp3}
\gll Komedyen-ler-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
comedian-\textsc{pl}-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}--\textsc{pl}\\
\glt Because of the northeaster, comedians' assistant felt chilly.

\ex \underline{Ungrammatical, SG attractor} \label{exp4}
\gll Komedyen-in yard{\i}mc{\i}-s{\i} poyraz-dan dolayi \"{u}\c{s}\"{u}-d\"{u}-ler.\\
comedian-\textsc{gen} helper-\textsc{poss} northeaster-\textsc{abl} because.of feel.chilly-\textsc{pst}-\textsc{pl}\\
\glt Because of the northeaster, comedian's assistant felt chilly.

\end{xlist}
\end{exe}

As seen in the examples unlike Lago (2018)'s experimental items, all of
our items bear the \emph{-sI} possessive marker instead of the ambiguous
\emph{-I} one. As for the filler items, we could not used or adapt from
the original experimentsince the fillers of the original study were not
online. We have used two types filler sentences: a grammatical ones
where the verb bears plural agreement (\ref{fillera}), and an
ungrammatical one where verb does not bear plural agreement
(\ref{fillerb}). We wanted to nullify a possible strategy by the
participants where they associate the sentence-final morpheme directly
with the acceptability, and disregard other elements in the sentences
when answering questions.

\begin{exe}
\ex
\begin{xlist}
\ex \label{fillera}
\gll Adam-{\i}n anne-si fena-la\c{s}-{\i}nca inek kurban et-ti-ler.\\
man-\textsc{gen} mother-\textsc{poss} bad-\textsc{vrb}-\textsc{cvb} cow sacrifice do-\textsc{pst}-\textsc{pl}\\
\glt When his mother got ill, (they) sacrificed a cow.
\ex \label{fillerb}
\gll *Pizzac{\i}-n{\i}n kurye-si t\"{o}kezle-yince sos-lar yer-e sa\c{c}-t{\i}.\\
pizzaria-\textsc{gen} courier-\textsc{poss} trip-\textsc{cvb} sauce-\textsc{pl} floor-\textsc{dat} scatter-\textsc{pst}\\
\glt Intended: When the pizza boy tripped, sauces scattered around. 
\end{xlist}
\end{exe}

All of our data, experimental materials, our experiment design, and as
well as our fillers can be found at the Center for Open Science
Framework website (\url{https://osf.io/}).

\hypertarget{participants-and-procedure}{%
\subsection{Participants and
Procedure}\label{participants-and-procedure}}

One hundred seven Turkish speakers with mean age of X were recruited
from the Bogazici University in \{.I\}stanbul. We did not collect
participants' knowledge of other languages; however, we ensured that
Turkish is their native language and they predominantly used in their
daily lives. In the experiments, participants are asked to judge the
experimental and filler sentences whether or not they sound acceptable
in Turkish. All of the sentences were presented one word at a time in
the center area of the screen for 500 ms per word unlike Lago (2018) and
Wagers et al. (2009), in which researches used 300 ms visual
presentation per word. Experiment was run on a web-based platform Ibex
Farm, and all of the documentation can be found in our osf and github
page.

Before the experiment, they have been instructed to give accurate and
quick answers with their own intuition, and they were also notified
about the time limit for answering. At the start of the experiment they
were given 4 practice items with feedbacks.

What to write about analyze?

In \textsc{Figure} (\ref{fig:replication}), y-axis shows proportion of
``acceptable'' answers, and x-axis indicates whether or not the
sentences in that group is grammatical. Moreover, linetypes indicates an
attractor noun with overt plural morphology. As seen from the figure,
22\% of the sentences with plural attractors and singular verb were
accepted by the participants following the findings of Lago (2018). We
also see a number attraction rate of 10\% which was already shown in
Lago (2018) with close results.

In \textsc{Table} (\ref{tab:replication}),
\ldots{}\ldots{}\ldots{}\ldots{}

\begin{figure}[H]
  \begin{floatrow}
    \ffigbox{%

\begin{flushright}\includegraphics{output/figures/unnamed-chunk-1-1} \end{flushright}
    }{\caption{A figure}}

    \btabbox{%

\begin{tabular}{l|r|r|r}
\hline
  & mpg & cyl & disp\\
\hline
Mazda RX4 & 21.0 & 6 & 160\\
\hline
Mazda RX4 Wag & 21.0 & 6 & 160\\
\hline
Datsun 710 & 22.8 & 4 & 108\\
\hline
Hornet 4 Drive & 21.4 & 6 & 258\\
\hline
Hornet Sportabout & 18.7 & 8 & 360\\
\hline
Valiant & 18.1 & 6 & 225\\
\hline
\end{tabular}
    }{\caption{A table}}
  \end{floatrow}
\end{figure}

@@

@@

\leavevmode\hypertarget{ref-Wagers2009}{}%
Wagers, M. W., E. F. Lau, and C. Phillips. 2009. Agreement attraction in
comprehension: Representations and processes. Journal of Memory and
Language 61:206--237.
